`gosset`: An R package for analysis and synthesis of ranking data in agricultural

### 2022-06-25 inst/paper/paper.Rmd

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural
  experimentation'
abstract: null
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    number_sections: no
    keep_tex: no
latex_engine: pdflatex
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: citationstyle.csl
header-includes:
- \usepackage{pdfpages}
- \usepackage{caption}
- \usepackage{xcolor}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{font=small}
---

@@

```{r , message=FALSE, eval=FALSE, echo=TRUE}
# temp <- temperature(covar[, c("longitude","latitude")], 
#                     day.one = covar[, "planting_date"],
#                     span = 80)
# 
# head(temp[, 1:2])
```

@@

Table 3 shows the results of reliability for the evaluated common bean varieties in each of 
the resulting nodes of the Plackett-Luce tree.

@@

>>>>

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural
  experimentation'
abstract: null
output:
  word_document:
  pdf_document:
    fig_caption: yes
    number_sections: no
    keep_tex: no
  reference_docx: paper_template_format.docx
latex_engine: pdflatex
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: citationstyle.csl
header-includes:
- \usepackage{pdfpages}
- \usepackage{caption}
- \usepackage{xcolor}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{font=small}
---

@@

```{r , message=FALSE, eval=FALSE, echo=TRUE}
# temp <- temperature(covar[, c("longitude","latitude")],
#                     day.one = covar[, "planting_date"],
#                     span = 80)
#
# head(temp[, 1:2])
```
=======
To consider the effect of climatic factors on variety performance, we used temperature-derived covariates to fit a
Plackett-Luce tree. For brevity, we used the variables maximum nighttime temperature (maxNT) and  maximum daytime temperature, but more variables can be used in a Plackett-Luce tree. Temperature data were obtained from the AgERA5 dataset [@boogaard_2020], using the R package *ag5Tools* [@ag5tools]. The temperature data downloaded from AgERA5 were used for computing the climatic variables with the package *climatrends* [@climatrends]. In this case, we only use the rankings corresponding to the overall performance of varieties.
>>>>>>> Stashed changes

@@

We can use the function ``reliability`` to compute the reliability of the evaluated common bean
varieties in each of the resulting nodes of the Plackett-Luce tree (Table 3).

@@

With the function ``crossvalidation`` we can validate the model.

```{r, message=FALSE, eval=TRUE, echo=FALSE}
nb_cv <- crossvalidation(R ~ .,
                         alpha = .6,
                         data = pld)

```
```{r cv, message=FALSE, eval=TRUE, echo=FALSE}

kable(nb_cv$coeffs[,c(1:4, 7, 8)], caption = "Results of 10-fold random cross-validation")
